Methods for Large Scale Learning to Rank

### 2014-09-09 report/Chapters/Results.tex
mooie plaatjes + in report

This chapter describes the results of the running time measurements of the cluster and baseline implementations as described in \ref{chap:implementation}.

>>>>

This chapter describes the results of the running time measurements of the cluster and baseline implementations as described in \ref{chap:implementation}.
\section{ListNet}
Figure
\begin{figure}
\centering
\includegraphics[trim=0cm 5cm 0cm 5cm, scale=0.7]{gfx/time_single.pdf}
\caption{Processing time of a single ListNet training iteration}
\label{fig:listnet_train_time}
\end{figure}

\begin{figure}
\centering
\includegraphics[trim=0cm 5cm 0cm 5cm, scale=0.7]{gfx/time_single_logx.pdf}
\caption{Processing time of a single ListNet training iteration on a logarithmic scale}
\label{fig:listnet_train_time_log}
\end{figure}

\begin{figure}
\centering
\includegraphics[trim=0cm 5cm 0cm 5cm, scale=0.7]{gfx/throughput_single_logx.pdf}
\caption{Throughput of a ListNet training iteration}
\label{fig:listnet_throughput}
\end{figure}
